Digital History in Finland, 1488-1828

### 2016-10-04 inst/examples/manuscript-krakow.Rmd
Rmd update

### Printing of natural science in different languages in Turku

```{r topics-104, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
sel = c("luonnontieteet","matematiikka","fysiikka","kemia","tähtitiede","maantiede","geodesia","geofysiikka","meteorologia")
# Selected catalogue with selected topics
df = dfl
df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
df <- df %>% filter(hit)
df <- df %>% group_by(publication_decade, language) %>%
             summarise(n = n(),
                 paper = sum(paper, na.rm = TRUE))

# PAPER CONSUMPTION
theme_set(theme_bw(20))
p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_bar(aes(fill = language), position = "stack", stat = "identity") +                     
       xlab("Publication year") +
       ylab("Paper consumption") +
       ggtitle(paste("Paper (", paste(sel, collapse = ";"), ")", sep = ""))
print(p)

```
---

@@

  # PAPER CONSUMPTION
  theme_set(theme_bw(20))
  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
       xlab("Publication year") +
       ylab("Paper consumption") +
       ggtitle(place) +
       xlim(c(years[[1]], years[[2]]))
  pics[[place]] <- p

@@

```{r ktopic2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}

catalogue <- "Kungliga"
years <- c(1640, 1828)
sel =  tolower(c("Idé- och lärdomshistoria", "Antiken", "Historia", "Militärhistoria"))
places <- c("Stockholm", "Lund", "Greifswald", "Uppsala", "Tartu")

@@

  # PAPER CONSUMPTION
  theme_set(theme_bw(20))
  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
       xlab("Publication year") +
       ylab("Paper consumption") +
       ggtitle(place) +
       xlim(c(years[[1]], years[[2]]))
  pics[[place]] <- p

@@

  # PAPER CONSUMPTION
  theme_set(theme_bw(20))
  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
       xlab("Publication year") +
       ylab("Paper consumption") +
       ggtitle(place) +
       xlim(c(years[[1]], years[[2]]))
  pics[[place]] <- p

@@

```{r ktopic7, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}

catalogue <- "Kungliga"
years <- c(1640, 1828)
sel =  tolower(c("Politisk filosofi","Ekonomiska förhållanden"," Nationalekonomi","Lantbruksekonomi","Ekonomi","Penningväsen","Penningvärde","Kreditväsen","Penningförfalskning","Moral","Pedagogik","Uppfsotringsverket","Uppfostran","Barnuppfostran","Jordbruk","Jordbrukslära","Jordbrukspolitik","Fiske"))
places <- c("Stockholm", "Lund", "Greifswald", "Uppsala", "Tartu")

@@

  # PUBLISHER COUNT
  n = sapply(split(dfs$publisher, dfs$publication_year), function (x) {
         length(unique(na.omit(x)))})
  df = data.frame(year = names(n), n = unname(n))
  if (nrow(df) > 1) {
    p = ggplot(df, aes(x = year, y = n)) +
        geom_bar(stat = "identity") +
       ggtitle(paste("Publishers:", catalogue, place)) +
       scale_x_discrete(breaks = seq(min(sel.years), max(sel.years), 10))
  } else {
    p <- ggplot() + ggtitle("Insufficient data")
  }
  pics[[paste(place, catalogue, sep = "-")]] <- p
}
}

>>>>

### Printing of natural science in different languages in Fennica/Turku

```{r topics-104, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
sel <- c("luonnontieteet","matematiikka","fysiikka","kemia","tähtitiede","maantiede","geodesia","geofysiikka","meteorologia")
# Selected catalogue with selected topics
#catal <- "Fennica"
#myplace <- "Turku" 
#df <- df0 %>% filter(catalog == catal & publication_place == myplace)
df <- dfl

df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
df <- df %>% filter(hit)
df <- df %>% group_by(publication_decade, language) %>%
             summarise(n = n(),
                 paper = sum(paper, na.rm = TRUE))
# Only use the first listed language for a doc
# df$language <- sapply(strsplit(df$language, ";"), function (x) {x[[1]]})

  if (nrow(df) > 0) {		       
    # PAPER CONSUMPTION
    theme_set(theme_bw(20))
    p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_bar(aes(fill = language), position = "stack", stat = "identity") +                     
       xlab("Publication year") +
       ylab("Paper consumption") +
       ggtitle(paste("Paper (", paste(sel, collapse = ";"), ")", sep = ""))
    print(p)
  } else {
    p <- ggplot() + ggtitle(paste(place, "; no hits"))
  }

@@

  if (nrow(df) > 0) {		       
    # PAPER CONSUMPTION
    theme_set(theme_bw(20))
    p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
       xlab("Publication year") +
       ylab("Paper consumption") +
       ggtitle(place) +
       xlim(c(years[[1]], years[[2]]))
  } else {
    p <- ggplot() + ggtitle(paste(place, "; no hits"))
  }

  pics[[place]] <- p

@@

```{r ktopic2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}
catalogue <- "Kungliga"
years <- c(1640, 1828)
sel <- tolower(c("Idé- och lärdomshistoria", "Antiken", "Historia", "Militärhistoria"))
places <- c("Stockholm", "Lund", "Greifswald", "Uppsala", "Tartu")

@@

  if (nrow(df) > 0) {
    # PAPER CONSUMPTION
    theme_set(theme_bw(20))
    p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
       xlab("Publication year") +
       ylab("Paper consumption") +
       ggtitle(place) +
       xlim(c(years[[1]], years[[2]]))
  } else {
    p <- ggplot() + ggtitle(paste("no hits"))
  }

  pics[[place]] <- p

@@

  # PAPER CONSUMPTION
  if (nrow(df) > 0) {
    theme_set(theme_bw(20))
    p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
       xlab("Publication year") +
       ylab("Paper consumption") +
       ggtitle(place) +
       xlim(c(years[[1]], years[[2]]))
  } else {
    p <- ggplot() + ggtitle(paste("no hits"))
  }

  pics[[place]] <- p

@@

```{r ktopic7, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}
catalogue <- "Kungliga"
years <- c(1640, 1828)
sel =  tolower(c("Politisk filosofi","Ekonomiska förhållanden"," Nationalekonomi","Lantbruksekonomi","Ekonomi","Penningväsen","Penningvärde","Kreditväsen","Penningförfalskning","Moral","Pedagogik","Uppfsotringsverket","Uppfostran","Barnuppfostran","Jordbruk","Jordbrukslära","Jordbrukspolitik","Fiske"))
places <- c("Stockholm", "Lund", "Greifswald", "Uppsala", "Tartu")

@@

  # PUBLISHER COUNT
  n <- sapply(split(dfs$publisher, dfs$publication_year), function (x) {
         length(unique(na.omit(x)))})
  df <- data.frame(year = names(n), n = unname(n))
  if (nrow(df) > 1) {
    p = ggplot(df, aes(x = year, y = n)) +
        geom_bar(stat = "identity") +
       ggtitle(paste("Publishers:", catalogue, place)) +
       scale_x_discrete(breaks = seq(min(sel.years), max(sel.years), 10))
  } else {
    p <- ggplot() + ggtitle("Insufficient data")
  }
  pics[[paste(place, catalogue, sep = "-")]] <- p
}
}
